Test if analytic derivation of geodesic distance for curves from sim_functional_data.R

### 2019-05-16 test_analytic_geodesic_distance.Rmd
fix webpage

```{r}
library(reticulate)
# sometimes reticulate requires specific instruction on where to find your python
# first call Sys.which("python") and then copy that path into 
#use_python('/Users/suswei/anaconda3/bin/python',required=TRUE)
use_python('/Users/UQAM/anaconda3/bin/python',required=TRUE)
get_min_num_neighbors = import_from_path("get_min_num_neighbors",path='.')
getIsomapGdist = import_from_path("getIsomapGdist",path='.')

>>>>

```{r}
library(reticulate)
# sometimes reticulate requires specific instruction on where to find your python
# first call Sys.which("python") and then copy that path into

#use_python('/Users/suswei/anaconda3/bin/python',required=TRUE)
use_python('/Users/UQAM/anaconda3/bin/python',required=TRUE)

get_min_num_neighbors = import_from_path("get_min_num_neighbors",path='.')
getIsomapGdist = import_from_path("getIsomapGdist",path='.')
